---
title: "EWSFLI1 TurboID"
author: "Aiola Stoja"
date: "2023-08-14"
output: html_document
---
<style type="text/css">
   .main-container {max-width: 100%;}
   .row {display: flex;}
   .column {flex: 50%;}
</style>

```{r setup packages, include=FALSE}

library(readxl)
library(eulerr)
library(dplyr)
library(VennDiagram)
library(devtools)
#install_github("wjawaid/enrichR")
library(enrichR)
library(ggpubr)
library(tidyr)
library(kableExtra)

```


```{r setup reading file, include=FALSE}

my_data <- as.list(read_xlsx("UniqueGenes.xlsx"))

naomit_mydata <- lapply(my_data, function(x) x[!is.na(x)])

```

# EWSFLI1 vs EWS TurboID Venn Diagram

```{r venn diagram ews vs ewsfli1 only}

genes.venn <- euler(naomit_mydata)
plot(genes.venn, quantities = TRUE)

```

```{r extracting venn partitions, include=FALSE}

VennPartition<-get.venn.partitions(naomit_mydata) %>% dplyr::as_tibble()


listVennPartition <- setNames(as.list(VennPartition$..values..), VennPartition$..set..)


```


```{r setup enrichr , include=FALSE}

websiteLive <- getOption("enrichR.live")
if (websiteLive) {
    listEnrichrSites()
    setEnrichrSite("Enrichr") # Human genes   
}

if (websiteLive) dbs <- listEnrichrDbs()

dbs <- c("GO_Molecular_Function_2015", "GO_Cellular_Component_2015", "GO_Biological_Process_2015")

if (websiteLive) {
    enrichedEWSxEWSFLI1 <- enrichr(listVennPartition[["EWS∩EWS::FLI1"]], dbs)
}

if (websiteLive) {
    enrichedEWSFLI1 <- enrichr(listVennPartition[["(EWS::FLI1)∖(EWS)"]], dbs)
}

if (websiteLive) {
    enrichedEWS <- enrichr(listVennPartition[["(EWS)∖(EWS::FLI1)"]], dbs)
}



```

<div class = "row">
<div class = "column">

## EWSFLI1 and EWS shared gene GO terms {.tabset}

### Biological Process

```{r enrichr EWSxEWSFLI1 Biological Process , echo=FALSE, message=FALSE, warning=FALSE}



#Biological Process

if (websiteLive) {
    plotEnrich(enrichedEWSxEWSFLI1$GO_Biological_Process_2015, showTerms = 20, numChar = 40, y = "Count", orderBy = "Adjusted.P.value", title = "EWS and EWSFLI1 shared Enrichr: GO Biolog Process")
}
```

### Molecular Function

```{r enrichr EWSxEWSFLI1 Molecular Function , echo=FALSE, message=FALSE, warning=FALSE}



#Molecular Function

if (websiteLive) {
    plotEnrich(enrichedEWSxEWSFLI1$GO_Molecular_Function_2015, showTerms = 20, numChar = 40, y = "Count", orderBy = "Adjusted.P.value", title = "EWS and EWSFLI1 shared Enrichr: GO Molec Function")
}
```

### Cellular component

```{r enrichr EWSxEWSFLI1 Cellular Component, echo=FALSE, message=FALSE, warning=FALSE}


#Cellular component

if (websiteLive) {
    plotEnrich(enrichedEWSxEWSFLI1$GO_Cellular_Component_2015, showTerms = 20, numChar = 40, y = "Count", orderBy = "Adjusted.P.value", title = "EWS and EWSFLI1 shared Enrichr:GO Cell Component")
}

```

</div>

<div class = "column">

## EWSFLI1 unique gene GO terms {.tabset}

### Biological Process

```{r enrichr EWSFLI1 only Biological Process, echo=FALSE, message=FALSE, warning=FALSE}


#Biological Process
if (websiteLive) {
    plotEnrich(enrichedEWSFLI1$GO_Biological_Process_2015, showTerms = 20, numChar = 40, y = "Count", orderBy = "Adjusted.P.value", title = "EWSFLI1 Enrichr: Go Biolog Process")
}

```

### Molecular Function

```{r enrichr EWSFLI1 only Molecular Function, echo=FALSE, message=FALSE, warning=FALSE}


#Molecular Function
if (websiteLive) {
    plotEnrich(enrichedEWSFLI1$GO_Molecular_Function_2015, showTerms = 20, numChar = 40, y = "Count", orderBy = "Adjusted.P.value", title = "EWSFLI1 Enrichr: GO Molec Function")
}

```

### Cellular Component 

```{r enrichr EWSFLI1 only Cellular Component, echo=FALSE, message=FALSE, warning=FALSE}


#Cellular component
if (websiteLive) {
    plotEnrich(enrichedEWSFLI1$GO_Cellular_Component_2015, showTerms = 20, numChar = 40, y = "Count", orderBy = "Adjusted.P.value", title = "EWSFLI1 Enrichr: GO Cell Component")
}

```

</div>
</div>

<div class = "row">
<div class = "col-md-6">

## EWS unique gene GO terms {.tabset}

### Biological Process

```{r enrichr EWS only Biological process, echo=FALSE, message=FALSE, warning=FALSE}


#Biological Process
if (websiteLive) {
    plotEnrich(enrichedEWS$GO_Biological_Process_2015, showTerms = 20, numChar = 40, y = "Count", orderBy = "Adjusted.P.value", title = "EWS Enrichr: GO Biological Process")
}

```

### Molecular Function

```{r enrichr EWS only Molecular Function, echo=FALSE, message=FALSE, warning=FALSE}


#Molecular Function
if (websiteLive) {
    plotEnrich(enrichedEWS$GO_Molecular_Function_2015, showTerms = 20, numChar = 40, y = "Count", orderBy = "Adjusted.P.value", title = "EWS Enrichr: GO Molec Function")
}

```

### Cellular Component

```{r enrichr EWS only Cellular Component, echo=FALSE, message=FALSE, warning=FALSE}


#Cellular component
if (websiteLive) {
    plotEnrich(enrichedEWS$GO_Cellular_Component_2015, showTerms = 20, numChar = 40, y = "Count", orderBy = "Adjusted.P.value", title = "EWS Enrichr: GO Cell Component")
}

```

</div>

## Enrichr Terms and Associated Genes {.tabset .tabset-fade .tabset-pills}

### EWS {.tabset .tabset-fade .tabset-pills}

#### EWS GO Molecular Function

<div class = "col-md-6">

```{r enrichr gene tabular view; EWS only Molec Function, echo=FALSE, message=FALSE, warning=FALSE}



EWS_GOMolecFunct_DF <- enrichedEWS[["GO_Molecular_Function_2015"]] %>% 
  select(-c(Old.P.value, Old.Adjusted.P.value, Odds.Ratio, Combined.Score)) %>%
  arrange(Adjusted.P.value)

knitr::kable(EWS_GOMolecFunct_DF, col.names = gsub("[.]", " ", names(EWS_GOMolecFunct_DF)), caption = "EWS Unique Genes  GO Molecular Function") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")

```

#### EWS GO Cell Component {.active}

```{r enrichr gene tabular view; EWS only Cell Component, echo=FALSE, message=FALSE, warning=FALSE}

EWS_GOCellComponent_DF <- enrichedEWS[["GO_Cellular_Component_2015"]] %>% 
  select(-c(Old.P.value, Old.Adjusted.P.value, Odds.Ratio, Combined.Score)) %>%
  arrange(Adjusted.P.value)

knitr::kable(EWS_GOCellComponent_DF, col.names = gsub("[.]", " ", names(EWS_GOCellComponent_DF)), caption = "EWS Unique Genes  GO Cell Component") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")




```


#### EWS GO Biological Process {.active}


```{r enrichr gene tabular view; EWS only Biological Process, echo=FALSE, message=FALSE, warning=FALSE}


EWS_GOBiolgProcess_DF <- enrichedEWS[["GO_Biological_Process_2015"]] %>% 
  select(-c(Old.P.value, Old.Adjusted.P.value, Odds.Ratio, Combined.Score)) %>%
  arrange(Adjusted.P.value)

knitr::kable(EWS_GOBiolgProcess_DF, col.names = gsub("[.]", " ", names(EWS_GOBiolgProcess_DF)), caption = "EWS Unique Genes  GO Biological Process") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")





```


### EWSFLI1 {.active .tabset .tabset-fade .tabset-pills}

#### EWSFLI1 GO Molecular Function

```{r enrichr gene tabular view; EWSFLI1 only GO Molec Function, echo=FALSE, message=FALSE, warning=FALSE}


EWSFLI1_GOMolecularFunction_DF <- enrichedEWSFLI1[["GO_Molecular_Function_2015"]] %>% 
  select(-c(Old.P.value, Old.Adjusted.P.value, Odds.Ratio, Combined.Score)) %>%
  arrange(Adjusted.P.value)

knitr::kable(EWSFLI1_GOMolecularFunction_DF , col.names = gsub("[.]", " ", names(EWSFLI1_GOMolecularFunction_DF)), caption = "EWSFLI` Unique Genes  GO Molecular Function") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")



```



#### EWSFLI1 GO Cell Component

```{r enrichr gene tabular view; EWSFLI1 only GO Cell Component, echo=FALSE, message=FALSE, warning=FALSE}


EWSFLI1_GOCellComponent_DF <- enrichedEWSFLI1[["GO_Cellular_Component_2015"]] %>% 
  select(-c(Old.P.value, Old.Adjusted.P.value, Odds.Ratio, Combined.Score)) %>%
  arrange(Adjusted.P.value)

knitr::kable(EWSFLI1_GOCellComponent_DF , col.names = gsub("[.]", " ", names(EWSFLI1_GOCellComponent_DF)), caption = "EWSFLI1 Unique Genes  GO Cell Component") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")


```

#### EWSFLI1 GO Biolgical Process {.active}

```{r enrichr gene tabular view; EWSFLI1 only GO Biological Process, echo=FALSE, message=FALSE, warning=FALSE}


EWSFLI1_GOBiologProcess_DF <- enrichedEWSFLI1[["GO_Biological_Process_2015"]] %>% 
  select(-c(Old.P.value, Old.Adjusted.P.value, Odds.Ratio, Combined.Score)) %>%
  arrange(Adjusted.P.value)

knitr::kable(EWSFLI1_GOBiologProcess_DF , col.names = gsub("[.]", " ", names(EWSFLI1_GOBiologProcess_DF)), caption = "EWSFLI1 Unique Genes  GO Biological Process") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")


```


### EWSxEWSFLI1 shared  {.active .tabset .tabset-fade .tabset-pills}

#### EWSxEWSFLI1 GO Molecular Function

```{r enrichr gene tabular view; Shared GO Molec Function, echo=FALSE, message=FALSE, warning=FALSE}


Shared_GOMolecularProcess_DF <- enrichedEWSxEWSFLI1[["GO_Molecular_Function_2015"]] %>% 
  select(-c(Old.P.value, Old.Adjusted.P.value, Odds.Ratio, Combined.Score)) %>%
  arrange(Adjusted.P.value)

knitr::kable(Shared_GOMolecularProcess_DF , col.names = gsub("[.]", " ", names(Shared_GOMolecularProcess_DF)), caption = "Shared Genes  GO Molecular Process") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")


```

#### EWSxEWSFLI1 GO Cell Component


```{r enrichr gene tabular view; Shared GO Cell Component, echo=FALSE, message=FALSE, warning=FALSE}


Shared_GOCellComponent_DF <- enrichedEWSxEWSFLI1[["GO_Cellular_Component_2015"]] %>% 
  select(-c(Old.P.value, Old.Adjusted.P.value, Odds.Ratio, Combined.Score)) %>%
  arrange(Adjusted.P.value)

knitr::kable(Shared_GOCellComponent_DF , col.names = gsub("[.]", " ", names(Shared_GOCellComponent_DF)), caption = "Shared Genes  GO Cell Component") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")


```


#### EWSxEWSFLI1 GO Biological Process {.active}

```{r enrichr gene tabular view; Shared GO Biological Process, echo=FALSE, message=FALSE, warning=FALSE}


Shared_GOBiologProcess_DF <- enrichedEWSxEWSFLI1[["GO_Biological_Process_2015"]] %>% 
  select(-c(Old.P.value, Old.Adjusted.P.value, Odds.Ratio, Combined.Score)) %>%
  arrange(Adjusted.P.value)

knitr::kable(Shared_GOBiologProcess_DF , col.names = gsub("[.]", " ", names(Shared_GOBiologProcess_DF)), caption = "Shared Genes  GO Biological Process") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")


```



</div>
</div>

<div class = "row">
<div class = "column">

# Comparing siRNA screen genes with EWSFLI1, EWS TurboID results

```{r Venn Diagram including siRNA screen, echo=FALSE, message=FALSE, warning=FALSE}

siRNAscreen <- read_xlsx("siRNA screen_hits (2).xlsx")

my_data$siRNA_genes <- siRNAscreen$`Gene Symbol...3`

naomit_datawithsiRNA<-lapply(my_data, function(x) x[!is.na(x)])

siRNAxTurboID.venn <- euler(naomit_datawithsiRNA)
plot(siRNAxTurboID.venn, quantities = TRUE)



```



```{r extracting venn partitions with siRNA, include=FALSE}

VennPartitionsiRNA<-get.venn.partitions(naomit_datawithsiRNA) %>% dplyr::as_tibble()

cutoff1.5onlyVenn <- my_data[-3]

VennPartitionssiRNAcutoff1.5<- get.venn.partitions(cutoff1.5onlyVenn) %>% dplyr::as_tibble()

listVennPartitionsiRNA <- setNames(as.list(VennPartitionsiRNA$..values..), VennPartitionsiRNA$..set..)
listVennPartitionsCutoff1.5 <- setNames(as.list(VennPartitionssiRNAcutoff1.5$..values..), VennPartitionssiRNAcutoff1.5$..set..)

```

</div>

<div class = "column">


## Shared genes from siRNA screen  {.tabset}

### All Shared (23)

```{r venn partitions siRNA gene tabular view; siRNAxEWSFLI1xEWS, echo=FALSE, message=FALSE, warning=FALSE}


siRNAxEWSFLI1xEWS_GenesDF <- as.data.frame(listVennPartitionsiRNA[["EWS∩EWS::FLI1∩siRNA_genes"]])

siRNAxEWSFLI1xEWS_GenesDF<- rename(siRNAxEWSFLI1xEWS_GenesDF, SharedGenes = starts_with("list"))


knitr::kable(siRNAxEWSFLI1xEWS_GenesDF , col.names = gsub("[.]", " ", names(siRNAxEWSFLI1xEWS_GenesDF)), caption = "siRNAxEWSFLI1xEWS  shared genes") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")


```


### siRNA and EWSFLI1 shared (37)

```{r venn partitions siRNA gene tabular view; siRNAxEWSFLI1, echo=FALSE, message=FALSE, warning=FALSE}


siRNAxEWSFLI1_GenesDF <- as.data.frame(listVennPartitionsiRNA[["(EWS::FLI1∩siRNA_genes)∖(EWS)"]])

siRNAxEWSFLI1_GenesDF<- rename(siRNAxEWSFLI1_GenesDF, SharedGenes = starts_with("list"))


knitr::kable(siRNAxEWSFLI1_GenesDF , col.names = gsub("[.]", " ", names(siRNAxEWSFLI1_GenesDF)), caption = "siRNAxEWSFLI1  shared genes") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")


```


### siRNA and EWS shared (17)

```{r venn partitions siRNA gene tabular view; siRNAxEWS, echo=FALSE, message=FALSE, warning=FALSE}


siRNAxEWS_GenesDF <- as.data.frame(listVennPartitionsiRNA[["(EWS∩siRNA_genes)∖(EWS::FLI1)"]])

siRNAxEWS_GenesDF<- rename(siRNAxEWS_GenesDF, SharedGenes = starts_with("list"))


knitr::kable(siRNAxEWS_GenesDF , col.names = gsub("[.]", " ", names(siRNAxEWS_GenesDF)), caption = "siRNAxEWS shared genes") %>%
   kable_styling("striped", full_width = F) %>% 
 scroll_box(width = "700px", height = "300px")


```



</div>
</div>

```{r Venn Diagram including siRNA screen cutoff -1.5, include = FALSE}


my_data$siRNA_genes_cutoff1.5 <- siRNAscreen$`Gene Symbol...14`

naomit_datawithsiRNAcutoff1.5<-lapply(my_data, function(x) x[!is.na(x)])

siRNALowerCutoffxTurboID.venn <- euler(naomit_datawithsiRNAcutoff1.5)
plot(siRNALowerCutoffxTurboID.venn, quantities = TRUE)



```



